---
title:  607_Project-3-DS-Skills-Daniel Thonn
output: html_document
course: R-607 CUNY MSDA program
reference-1: "http//www.cs.ukzn.ac.za/~hughm/dm/content/slides06.pdf"
reference-2: "http//www.rdatamining.com/examples/decision-tree"


---

# Assignment: 607_Project-3-DS-Skills-Daniel Thonn

Summary of Assignment
This project involes downloading Data Science skills from the internet then processing and presenting the data

This Assignment requires the following:

1). R-Studio

The following R-packages are used:
1.rpart
2.party
3.randomForest 

Steps to reproduce:
1). run the R-Studio file: R_607_Project_3a_DS_Skils_Daniel_Thonn.Rmd


Setting up and Preparing the Environment

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=TRUE}

#packages and libraries

#library for building basic decision tree
library(rpart)

#library for ctree decision tree
#install.packages("party")
library(party)

#library for randomForest decision tree
#install.packages("randomForest")
library(randomForest)

#install.packages("dbConnect")
library(dbConnect) 

#install.packages("gplot2")
library(ggplot2)

#install.packages("tidyr")
library(tidyr)
library(dplyr)
library(knitr)


```

# Retreive data from database

```{r, echo=TRUE}

username = 'data607' 
password = 'project3' 
dbname = 'ds_skills' 
host = 'data607-project3.ce2dfe0qxt5q.us-west-2.rds.amazonaws.com' 
myDb = dbConnect(MySQL(), user=username, password=password, dbname=dbname, host=host) 
 
 
qryString = 'SELECT jobs.post_id, role_desc, city, state, keyword_desc  
             FROM jobs 
             INNER JOIN locations 
             ON jobs.loc_id = locations.loc_id 
             INNER JOIN roles 
             ON jobs.role_id = roles.role_id 
             INNER JOIN post_keys 
             ON jobs.post_id = post_keys.post_id  
             INNER JOIN  keywords 
             ON post_keys.key_id = keywords.key_id 
             ;' 
 
 
selectQry = dbSendQuery(myDb, qryString) 
results = fetch(selectQry, n = -1) 

#results
head(results)
#str(results)

```

```{r, echo=TRUE}
# Test Plots
#ggplot(data=results, aes(x=role_desc, y=keyword_desc, group=role_desc)) + geom_line()

#ggplot(data=results, aes(x=role_desc, y=city),group=role_desc) + geom_line()

#ggplot(data=results, aes(x=role_desc, y=keyword_desc)) + geom_line()

#ggplot() + geom_line(results, aes(x="role_desc", y="keyword_desc", group="role_desc"))

#ggplot() + geom_line(results, aes(x="role_desc", y="keyword_desc"))

```

```{r, echo=TRUE}
results1 <- select(results, role_desc, keyword_desc)

library(plyr)

results2 <- count(results1, c("role_desc", "keyword_desc")) 
#results2

#library(tidyr) 

results3 <- spread(results2, keyword_desc, freq) 
#results3

results3[is.na(results3)] <- 0 
#results3

names(results3) <- sub(" ", "", names(results3))
names(results3) <- sub(" ", "", names(results3))
results3$role_desc<-as.factor(results3$role_desc)

```




```{r, echo=TRUE}
## This section needs to be adjusted

#This section creates a table of non-distinct role_desc vs keyword_desc 

role_vs_Keyword_a <- results %>%
  select(role_desc,keyword_desc) 


#list(role_vs_Keyword_a)
head(role_vs_Keyword_a)
#role_vs_Keyword_a

#str(role_vs_Keyword_a)

role_vs_Keyword_b <- role_vs_Keyword_a
#role_vs_Keyword_b
role_vs_Keyword_b2 <- role_vs_Keyword_b
head(role_vs_Keyword_b2)
role_vs_Keyword_b2$row <- rep(1,nrow(role_vs_Keyword_b2))
role_vs_Keyword_b2$row2 <- 1:nrow(role_vs_Keyword_b2)
#role_vs_Keyword_b2

# Spread keyword values to columns
wide <- spread(role_vs_Keyword_b2,keyword_desc,row)

head(wide)

#wide

#str(wide)

wide_2 <- wide

#cleanup data frame:
wide_2[is.na(wide_2)] <- 0

#head(wide_2)

#wide_2
head(wide_2)
#str(wide_2)
#names(wide_2)
#wide_2

# Cleanup dataframe
wide_2$role_desc<-as.factor(wide_2$role_desc)
names(wide_2) <- sub(" ", "", names(wide_2))
names(wide_2) <- sub(" ", "", names(wide_2))

#names(wide_2)
#head(wide_2)
wide_3 <- subset(wide_2,select= -c(row2))
head(wide_3)


#Create and plot ctree of dataframe
target2 <- role_desc ~ .
cdt2 <- ctree(target2,wide_3)
#cdt2
plot(cdt2,type="simple")

#names(wide_2)
head(wide_2)
#str(wide_2)
#wide_2

#Create and plot ctree of dataframe
#skill_ctree <- ctree(role_desc ~ r + cassandra + d3, data=wide_2)
skill_ctree <- ctree(role_desc ~ excel + hadoop + sql, data=wide_3)
plot(skill_ctree)

skill_ctree2 <- ctree(role_desc ~ sql + java + python + scala + hive, data=wide_3)
#summary(iris$Species)
plot(skill_ctree2)

# Predict by Random Forest Method
#wide_3
names(wide_3)
#wide_2$role_desc
#wide_2$hadoop

# Create a predictive model of the data - rf
rf <- randomForest(target2,data=wide_3,ntree=1000,proximity=TRUE)
#table(predict(rf),wide_2$role_desc)

#names(wide_3)
newdata <- data.frame(r=1,
                      cassandra = 0,
                      d3 = 0,
                      d3.js=0,
                      excel=1,
                      flume = 0,
                      hadoop=1,
                      hbase = 0,
                      hive = 0,
                      java = 1,
                      mahout = 0,
                      mapreduce = 0,
                      matlab = 0,
                      mongodb = 0,
                      nosql = 1,
                      oozie = 0,
                      pig = 0,
                      python = 1,
                      ruby = 0,
                      sas = 1,
                      scala = 0,
                      shark = 0,
                      spark = 1,
                      spss = 0,
                      sql = 1,
                      tableau = 0
                    )


p <- predict(rf,newdata)

p

```



#END
