---
title:  607_Project-3-DS-Skills-Daniel Thonn
output: html_document
course: R-607 CUNY MSDA program
reference-1: "http//www.cs.ukzn.ac.za/~hughm/dm/content/slides06.pdf"
reference-2: "http//www.rdatamining.com/examples/decision-tree"


---

# Assignment: 607_Project-3-DS-Skills-Daniel Thonn

Summary of Assignment
This project involes downloading Data Science skills from the internet then processing and presenting the data

This Assignment requires the following:

1). R-Studio

The following R-packages are used:
1.rpart
2.party
3.randomForest 

Steps to reproduce:
1). run the R-Studio file: R_607_Project_3a_DS_Skils_Daniel_Thonn.Rmd


Setting up and Preparing the Environment

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=TRUE}

#packages and libraries

#library for building basic decision tree
library(rpart)

#library for ctree decision tree
#install.packages("party")
library(party)

#library for randomForest decision tree
#install.packages("randomForest")
library(randomForest)

#install.packages("dbConnect")
library(dbConnect) 

#install.packages("gplot2")
library(ggplot2)

library(tidyr)
library(dplyr)
library(knitr)


```

# Retreive data from database

```{r, echo=TRUE}

username = 'data607' 
password = 'project3' 
dbname = 'ds_skills' 
host = 'data607-project3.ce2dfe0qxt5q.us-west-2.rds.amazonaws.com' 
myDb = dbConnect(MySQL(), user=username, password=password, dbname=dbname, host=host) 
 
 
qryString = 'SELECT jobs.post_id, role_desc, city, state, keyword_desc  
             FROM jobs 
             INNER JOIN locations 
             ON jobs.loc_id = locations.loc_id 
             INNER JOIN roles 
             ON jobs.role_id = roles.role_id 
             INNER JOIN post_keys 
             ON jobs.post_id = post_keys.post_id  
             INNER JOIN  keywords 
             ON post_keys.key_id = keywords.key_id 
             ;' 
 
 
selectQry = dbSendQuery(myDb, qryString) 
results = fetch(selectQry, n = -1) 
#results 

str(results)

```

```{r, echo=TRUE}
# Test Plots
#ggplot(data=results, aes(x=role_desc, y=keyword_desc, group=role_desc)) + geom_line()

#ggplot(data=results, aes(x=role_desc, y=city),group=role_desc) + geom_line()

#ggplot(data=results, aes(x=role_desc, y=keyword_desc)) + geom_line()

#ggplot() + geom_line(results, aes(x="role_desc", y="keyword_desc", group="role_desc"))

#ggplot() + geom_line(results, aes(x="role_desc", y="keyword_desc"))

```

```{r, echo=TRUE}
## This section needs to be adjusted

#This section creates a table of distinct role_desc vs keyword_desc 
#role_vs_Keyword<-results %>%
 # select(role_desc,keyword_desc) %>%
  #group_by(role_desc, keyword_desc) %>%
  #count(role_desc, keyword_desc) %>%
  # spread(role_desc,n)
  #spread(keyword_desc,n)

# Note: this section needs to be pivoted with non-distinct role_desc vs keyword_desc
role_vs_Keyword<-results %>%
  select(role_desc,keyword_desc)

list(role_vs_Keyword)
str(role_vs_Keyword)

#table(role_vs_Keyword)



role_vs_Keyword_2 <- as.data.frame(role_vs_Keyword)
#str(role_vs_Keyword_2)
#role_vs_Keyword_2

# Crete and draw a decision tree using rpart
#target <- role_desc ~ .
#dt_1 <- rpart(target, role_vs_Keyword_2)
#plot(dt_1); text(dt_1)
dtm<-rpart(role_desc~., role_vs_Keyword_2, method="class", minsplit=4, minbucket=1)
plot(dtm); text(dtm)

#************

# Cleanup dataframe

role_vs_Keyword_3 <- role_vs_Keyword_2
#role_vs_Keyword_3
role_vs_Keyword_3[is.na(role_vs_Keyword_3)] <- 0
#role_vs_Keyword_3
for(i in c(2,2:ncol(role_vs_Keyword_3))) {
    role_vs_Keyword_3[,i] <- as.numeric(role_vs_Keyword_3[,i])}
role_vs_Keyword_3$role_desc<-as.factor(role_vs_Keyword_3$role_desc)
role_vs_Keyword_3$role_desc
str(role_vs_Keyword_3)
names(role_vs_Keyword_3) <- sub(" ", ".", names(role_vs_Keyword_3))
names(role_vs_Keyword_3) <- sub(" ", ".", names(role_vs_Keyword_3))
names(role_vs_Keyword_3) <- sub("\\++", "plusplus", names(role_vs_Keyword_3))
#names(role_vs_Keyword_3) 
role_vs_Keyword_3

#Create and plot ctree of dataframe
target2 <- role_desc ~ .
cdt2 <- ctree(target2,role_vs_Keyword_3)
#cdt2
plot(cdt2,type="simple")
#summary(iris$Species)
#plot(cdt,type="simple")

#Create and ctree of dataframe
skill_ctree <- ctree(role_desc ~ b.i. + tableau + hadoop, data=role_vs_Keyword_3)
#summary(iris$Species)
plot(skill_ctree)

# Predict by Random Forest Method
role_vs_Keyword_3
#names(role_vs_Keyword_3)
role_vs_Keyword_3$role_desc

rf <- randomForest(target2,data=role_vs_Keyword_3,ntree=1000,proximity=TRUE)
#summary(iris$Species)
table(predict(rf),role_vs_Keyword_3$role_desc)


```



#END
